Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-16 paper/paper.tex
Iterate Performance

\section{Performance \tbr}
\label{sec:performance}

@@

This section summarizes the core results of the evaluation of Spanner, i.e. the
latency and throughput performance as well as some results about availability
and the TrueTime API.

Table~\ref{tbl:performance-of-operations} summarizes the latency and throughput
performance of Spanner. 1D means one replica with commit wait disabled. Hence,
only write transactions are evaluated because commit wait is only involved in such
transactions. As we can see, the latency of all transaction types is almost stable
for an increasing number of replicas whereas the standard deviation decreases.
The throughput of read-only transaction increases with the number of replicas
because the number of spanservers increases (in the experiments, the number of
replicas and the number of spanservers were the same. The throughput of write
transactions also benefits from this fact. However, the number of write operations
to perform increases linearly with the number of replicas. Snapshot reads benefit
the most from the Spanner architecture. The throuhgput of snapshot reads increases
almost linear with the number of replicas.

The availability of Spanner is only affected if zones containing multiple leaders
are shut down without notifying the leader upfront. In this case, it takes Spanner
about 10s to recover full availability. If the leaders are notified to abdicate
before their zone is shut down, the availability stays almost unaffected. The same
if true if a zone without a leader is shut down.

Google also provided results for some experiments concerning TrueTime. All
assumptions Google made when designing Spanner would break if the local clock
drift would exceed $200\mu$s/sec. But Google found that clock issues are extremely
infrequent relative to more serious hardware problems, e.g. bad CPUs. Moreover,
Google provided empirical results on the values of $\epsilon$. Typically,
$\epsilon$ is never larger than 10ms. It decreases as the network infrastructure
is improved and increases if time masters go offline.

>>>>

\section{Performance}
\label{sec:performance}

@@

This section summarizes the core results of the evaluation of Spanner, i.e. the
latency and throughput performance as well as some results concerning availability
and the TrueTime API.

Table~\ref{tbl:performance-of-operations} summarizes the latency and throughput
performance of Spanner. 1D means one replica with Commit Wait disabled. Hence,
only write transactions are evaluated because Commit Wait is not involved in any
other type of transaction. As we can see, the latency of all transaction types is
almost stable for an increasing number of replicas whereas the standard deviation
decreases. The throughput of read-only transactions increases with the number of
replicas because the number of spanservers increases. In the experiments, the
number of replicas and the number of spanservers were equal. The throughput of write
transactions also benefits from this fact. However, the number of write operations
to perform increases linearly with the number of replicas. This explains why the
throughput of write transactions does not increase with the number of replicas.
Snapshot reads benefit the most from the Spanner architecture. The throughput of
snapshot reads increases almost linearly with the number of replicas.

The availability of Spanner is only affected if zones containing multiple leaders
are shut down without notifying the leaders upfront. In this case, it takes Spanner
about 10s to recover. If the leaders are notified to abdicate before their zone
is shut down, the availability is almost unaffected. The same is true if a zone
without a leader is shut down.

Google also provided empirical results about TrueTime. All assumptions Google
made while designing Spanner would be broken if the local clock drift of a machine
exceeds $200\mu$s/sec. But Google found that clock issues are extremely infrequent
relative to more serious hardware problems, e.g. bad CPUs. Moreover, Google
provided empirical results on the values of $\epsilon$. Typically, $\epsilon$ is
never larger than 10ms. It decreases as the network infrastructure is improved
and increases if time masters go offline.
